Robust Estimation, Prediction and Control with \\ Linear Dynamics and Generic Costs

### 2020-02-14 main.tex
Add supplmentary description

% Custom packages
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{blkarray}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{bm}
\usepackage{enumitem}
\usepackage{comment}
\def\sectionautorefname{Section}
\input{mathdef.tex}

@@

\paragraph{Outline}
In \autoref{sec:proof}, we provide a proof for every novel result introduced in this paper. \autoref{sec:tight-polytope} describes a better method of conversion from ellipsoid to polytope than that of \eqref{eq:polytope}. \autoref{sec:min-max-order} highlights the fact that robustness cannot be recovered by aggregating independent solutions to many optimal control problem. Finally, \autoref{sec:experimental-setting} gives additional details on the setting of our experiments.

@@

>>>>

% Custom packages
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{blkarray}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{bm}
\usepackage{enumitem}
\usepackage{comment}
\usepackage{listings}
\def\sectionautorefname{Section}
\input{mathdef.tex}

@@

\paragraph{Outline}
In \autoref{sec:proof}, we provide a proof for every novel result introduced in this paper. \autoref{sec:attachments} describes the attached video files and source code. \autoref{sec:tight-polytope} gives a better method of conversion from ellipsoid to polytope than that of \eqref{eq:polytope}. \autoref{sec:min-max-order} highlights the fact that robustness cannot be recovered by aggregating independent solutions to many optimal control problem. Finally, \autoref{sec:experimental-setting} provides additional details on the setting of our experiments.

@@

\section{Description of attached files}
\label{sec:attachments}

\paragraph{Videos}
The \texttt{video} folder contains videos comparing trajectories of the oracle planner and \autoref{alg:full}. The oracle planner has access to the true dynamics and follows aggressive trajectories that nearly saturate the collision constraints. In contrast, the \autoref{alg:full} produces more conservative trajectories. In the obstacle experiment, we show the confidence ellipsoid over $\theta = (\theta_x,\theta_y)$ in the right panel. In the driving experiment, we show the multi-model rejection and robust selection procedure through the display of several trajectory hulls for all possible destinations of the observed vehicles.

\paragraph{Source code}
We describe where the main contributions of this work are implemented in the attached code.
\begin{enumerate}
	\item The confidence ellipsoid \eqref{eq:confidence-ellipsoid} is implemented in the \texttt{ellipsoid()} method in \url{code/rl_agents/agents/tree_search/robust_epc.py}
	\item The corresponding polytope \eqref{eq:polytope} is implemented in the \texttt{polytope()} method of \url{code/rl_agents/agents/tree_search/robust_epc.py}
	\item The simple predictor of \eqref{eq:predictor-naive} is implemented in the \texttt{step\_simple\_predictor()} method of \url{code/rl_agents/agents/common/interval.py}
	\item The enhanced predictor of \eqref{eq:interval-predictor} is implemented in the \texttt{step\_interval\_predictor()} method of \url{code/rl_agents/agents/common/interval.py}
	\item The pessimistic reward of \eqref{eq:pessimistic-rewards} is implemented in the \texttt{pessimistic\_reward()} method of \url{code/obstacle_env/envs/obstacle.py} and the \texttt{check\_collision()} method of \url{code/highway_env/vehicle/uncertainty/prediction.py}
	\item The robust upper-bound of \eqref{eq:robust-b-values} is implemented in the \texttt{RobustNode} class of \url{code/rl_agents/agents/tree_search/robust.py}
\end{enumerate}
The experiments can be reproduced by running:
\lstset{language=bash}
\begin{lstlisting}
cd scripts
python experiments.py configs/<env>/env.json configs/<env>/agents/<agent>.json
\end{lstlisting}
